\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Spatiotemporal modeling of \emph{Mycobacterium tuberculosis} transmission risks using environmental, clinical, and patient movement data}

### 2023-08-08 doc/paper/supplements.tex

The diffusion constant $D$ is unknown but can be approximated using an empirical relationship between the eddy diffusion coefficient $K$ and the outdoor air exchange rate $AER$ (in air changes/h)
\begin{align}
    K = (0.52 \cdot AER + 8.61\cdot10^{-5}) \cdot V^{\frac{2}{3}},
\end{align}
where $V$ is the volume of the airspace (in m$^3$). We assume that $D \approx K$.

@@

\section{Estimation of infection risk in the primary care clinic}

@@

\subsection{Data and linkage}

@@

Face masks reduce the number of viral-laden aerosols that are exhaled into the air\cite{Milton2013PLoSPathogens,Leung2020NatMed} and should thus lower the generation of infectious quanta. The extent of the reduction is subject to uncertainty. A study with multidrug-resistant TB cases estimated a decrease of 56\% (95\%-CrI, 33\% to 70.5\%) when patients used surgical face masks\cite{Dharmadhikari2012AJRCCM}. This estimate was used by a modelling study to estimate the impact of mask wearing on \emph{Mtb} transmission in a primary care clinic. Therefore,, we model the reduction in infectious quanta through mask wearing with a Normal($\mu$ = 0.56, $\sigma$ = 0.11) truncated at 0 and 1. The effective quanta generation rate is thus $q$ times the reduction due to mask wearing. Again, we model what the risk of infection would have been without mask wearing by removing the reduction term from the model.

>>>>

The diffusion constant $D$ is unknown but can be approximated using an empirical relationship between the eddy diffusion coefficient $K$ and the outdoor air exchange rate $AER$ (in air changes/h)\cite{Cheng2011EnvSciTech}
\begin{align}
    K = (0.52 \cdot AER + 8.61\cdot10^{-5}) \cdot V^{\frac{2}{3}},
\end{align}
where $V$ is the volume of the airspace (in m$^3$). We assume that $D \approx K$.

@@

\section{Estimation of infection risk in the primary care clinic}\label{sec:estimation}

@@

@@

Face masks reduce the number of viral-laden aerosols that are exhaled into the air\cite{Milton2013PLoSPathogens,Leung2020NatMed} and should thus lower the generation of infectious quanta. The extent of the reduction is subject to uncertainty. A study with multidrug-resistant TB cases estimated a decrease of 56\% (95\%-CrI, 33\% to 70.5\%) when patients used surgical face masks\cite{Dharmadhikari2012AJRCCM}. This estimate was used by a modelling study to estimate the impact of mask wearing on \emph{Mtb} transmission in a primary care clinic. Therefore, we model the reduction in infectious quanta through mask wearing with a Normal($\mu$ = 0.56, $\sigma$ = 0.11) truncated at 0 and 1. The effective quanta generation rate is thus $q$ times the reduction due to mask wearing. Again, we model what the risk of infection would have been without mask wearing by removing the reduction term from the model.
